Online {\IterComp}

### 2017-11-16 motivation.tex
WORK

    \paragraph{Challenges of using real inputs online.} We could overcome the problems of representative inputs by just evaluating
    optimization sequences online while the application is being used.
    %Optimization sequences are compared based on how much faster the program becomes.
    This gives us live data but creates a new problems.
    With live data, we cannot just compare runtimes.
    When all of the optimization sequences are tested against the same inputs, it is just a matter of comparing runtimes.
    A shorter runtime for processing the same data means a more efficient binary.
    With live data, we cannot do this, each binary processes
    whatever the input happens to be.
    As an example, considering a sorting algorithm. To measure the efficiency of an optimization for the algorithm, we need to look at not just
    how long does the algorithm run but also how many items it processes per run. Simply comparing the running time of two invocations does not
    tell us which program version is faster, as the two invocations may not process the same number of items. As a result, we need another efficiency metric
    that only requires a single execution of an optimized binary with a single input.

>>>>

    \paragraph{Challenges of using real inputs online.} We could overcome the problems of representative inputs by just evaluating
    optimization sequences online while the application is being used.
    %Optimization sequences are compared based on how much faster the program becomes.
    This gives us live data but creates a new problems.
    With live data, we cannot just compare runtime.
    When all of the optimization sequences are tested against the same inputs, it is just a matter of comparing runtime.
    A shorter runtime for processing the same data means a more efficient binary.
    With live data, we cannot do this, each binary processes
    whatever the input happens to be.
    As an example, considering a sorting algorithm. To measure the efficiency of an optimization for the algorithm, we need to look at not just
    how long does the algorithm run but also how many items it processes per run. Simply comparing the running time of two invocations of two program versions does not
    tell us which program version is faster, as the two invocations may not process the same number of items in a production environment. As a result, we need another efficiency metric
    that only requires a single execution of an optimized binary with a single input.

### 2017-11-16 work.tex
WORK

    With similar metrics, what exactly is work depends on the application and is defined by the developer: SQL queries executed,
    transactions completed, bytes processed, etc. In our case, we need a similar but application-agnostic metric which correlates with what
    the developer considers useful work and is simple enough to be calculated online.

@@

    We selected the work contribution of each instruction type so that total work becomes an estimator of the runtime of the unoptimized
    program.
    %Our choice to associate work with unoptimized runtime is largely arbitrary but instinctively reasonable.
    Our choice to associate work with unoptimized runtime is largely for practical reasons but it is also instinctively reasonable.
    Unoptimized time is
    close to how the programmer understands the effort put by the computer. Using it as the work metric makes work efficiency (work per unit
    of time) an estimator of the speedup of the optimized version over the unoptimized version. While other ways of setting the instruction
    contributions might be better, our results in Section~\ref{sec:results} show that this simple definition of work produces good results.
    Using the experimental setup described in Section~\ref{sec:setup}, we run the unoptimized versions of the 10 benchmarks listed in
    Table~\ref{tab:kdatasets:training} with all 1,000 available inputs. For each run, we recorded execution time and dynamic counters for all instruction types\footnote{
    Dynamic instruction counts were obtained by using the classic block-frequency profiling.}.
    Similarly to prior work~\cite{giusto01,powell09,brandolese11}, we then applied linear regression to find the contribution of each
    instruction type that minimizes the error between measured runtime and work.
    %\footnote{The resulting regression model uses \FIXME{70}
    %different instruction types which make it too long to present here.}

>>>>

    With similar metrics, what exactly is work depends on the application and is defined by the developer: SQL queries executed,
    transactions completed, bytes processed, etc. In our case, we need a similar but \emph{application-agnostic} metric which correlates with what
    the developer considers useful work and is simple enough to be calculated online.

@@

    We selected the work contribution of each instruction type so that total work becomes an estimator of the runtime of the unoptimized
    program.
    %Our choice to associate work with unoptimized runtime is largely arbitrary but instinctively reasonable.
    Our choice to associate work with unoptimized runtime is largely for practical reasons but it is also instinctively reasonable.
    Unoptimized time is
    close to how the programmer understands the effort put by the computer. Using it as the work metric makes work efficiency (work per unit
    of time) an estimator of the speedup of the optimized version over the unoptimized version. While other ways of setting the instruction
    contributions might be better, our results in Section~\ref{sec:results} show that this simple definition of work produces good results.
    Using the experimental setup described in Section~\ref{sec:setup}, we run the unoptimized versions of the 10 benchmarks listed in
    Table~\ref{tab:kdatasets:training} with all 1,000 available inputs. For each run, we recorded execution time and dynamic counters for all instruction types\footnote{
    Dynamic instruction counts were obtained by using the classic block-frequency profiling~\cite{knuth73}.}.
    Similarly to prior work~\cite{giusto01,powell09,brandolese11}, we then applied linear regression to find the contribution of each
    instruction type that minimizes the error between measured runtime and work.
    %\footnote{The resulting regression model uses \FIXME{70}
    %different instruction types which make it too long to present here.}
